### 2016-07-04 main text/draft0.0.tex
draftv0.01

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amsmath}
%\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{mn2e}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
%\usepackage{booktabs,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{mwe}    % loads »blindtext« and »graphicx«
\usepackage{subfig}

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total\, gas }} $\ }
\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
\newcommand \halpha    {H$\alpha $}
\newcommand \um    {$\mu$m}
%\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \boldit {\textbf{\textit{}}}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \GALEX {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand{\sii}{S~{\textsc II}} 
\newcommand{\oiii}{O~{\textsc III}} 
\newcommand{\hi}{H~{\textsc I}\ }

\newcommand \aaj {A\&A}
\newcommand \aarv {A\&ARv}%: Astronomy and Astrophysics Review (the)
\newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
\newcommand \afz {Afz}%: Astrofizika
\newcommand \aj {AJ}%: Astronomical Journal (the)
\newcommand \apss {Ap\&SS}%: Astrophysics and Space Science
\newcommand \apj {ApJ}
\newcommand \apjs {ApJS}%: Astrophysical Journal Supplement Series (the)
\newcommand \araa {ARA\&A} %: Annual Review of Astronomy and Astrophysics
\newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
\newcommand \azh {Azh}%: Astronomicheskij Zhurnal
\newcommand \baas {BAAS}%: Bulletin of the American Astronomical Society
\newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
\newcommand \mnassa {MNASSA}%: Monthly Notes of the Astronomical Society of Southern Africa
\newcommand \mnras {MNRAS} %: Monthly Notices of the Royal Astronomical Society
%\newcommand {Nature}%(do not abbreviate)
\newcommand \pasj {PASJ}%: Publications of the Astronomical Society of Japan
\newcommand \pasp {PASP}%: Publications of the Astronomical Society of the Pacific
\newcommand \qjras {QJRAS}%: Quarterly Journal of the Royal Astronomical Society
\newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
%\newcommand {Science }%}%(do not abbreviate)
\newcommand \sva {SvA}%: Soviet Astronomy
\newcommand \aap {APP} %:American Academy of Pediatrics
\newcommand \apjl {ApJL} %:The Astrophysical Journal Letters

\begin{document}
% TITLE

\title{Data Mining in Nearby Galaxies}
\author{rahmani.sahar }
\date{\today}
\author[S. Rahmani, et. al.]{S.~Rahmani$^{1, 2}$\thanks{E-mail:
srahma49@uwo.ca}, H.~Teimoorinia$^{3}$, E.~Peeters$^{1, 2, 4}$, P.~Barmby$^{1, 2}$\\
$^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
$^{2}$Center for Planetary Science \& Exploration, Western University, London, ON N6A 3K7, Canada\\
$^{3}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada\\
$^{4}$SETI Institute, 189 Bernardo Avenue, Suite 100, Mountain View, CA 94043, USA}
\maketitle

@@

\import{../sections/}{caveat.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Summery
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{SUMMARY}

\section*{ACKNOWLEDGMENTS}
S.R., P.B., and E.P. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%biblio
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\bibliographystyle{mnras}
\bibliography{ref_mining.bib}
\import{../sections/}{app_2d.tex}

>>>>

\documentclass[useAMS,usenatbib]{mn2e}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
%\usepackage{booktabs,fixltx2e}
\usepackage[flushleft]{threeparttable}
\usepackage{mwe}    % loads »blindtext« and »graphicx«
\usepackage{subfig}

\newcommand \kpc        {\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total\, gas }} $\ }
\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
\newcommand \halpha    {H$\alpha $}
\newcommand \um    {$\mu$m}
%\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \boldit {\textbf{\textit{}}}
\newcommand \eqnprime {N^\prime}
\newcommand \Spitzer {{\it Spitzer }}
\newcommand \GALEX {GALEX }
\newcommand \Herschel {{\it Herschel }}
\newcommand \sii {[S~{\textsc II}]} 
\newcommand \oiii {[O~{\textsc III}]} 
\newcommand \hi {H~{\textsc I}\ }

\newcommand \aaj {A\&A}
\newcommand \aarv {A\&ARv}%: Astronomy and Astrophysics Review (the)
\newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
\newcommand \afz {Afz}%: Astrofizika
\newcommand \aj {AJ}%: Astronomical Journal (the)
\newcommand \apss {Ap\&SS}%: Astrophysics and Space Science
\newcommand \apj {ApJ}
\newcommand \apjs {ApJS}%: Astrophysical Journal Supplement Series (the)
\newcommand \araa {ARA\&A} %: Annual Review of Astronomy and Astrophysics
\newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
\newcommand \azh {Azh}%: Astronomicheskij Zhurnal
\newcommand \baas {BAAS}%: Bulletin of the American Astronomical Society
\newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
\newcommand \mnassa {MNASSA}%: Monthly Notes of the Astronomical Society of Southern Africa
\newcommand \mnras {MNRAS} %: Monthly Notices of the Royal Astronomical Society
\newcommand \pasj {PASJ}%: Publications of the Astronomical Society of Japan
\newcommand \pasp {PASP}%: Publications of the Astronomical Society of the Pacific
\newcommand \qjras {QJRAS}%: Quarterly Journal of the Royal Astronomical Society
\newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
\newcommand \sva {SvA}%: Soviet Astronomy
\newcommand \aap {APP} %:American Academy of Pediatrics
\newcommand \apjl {ApJL} %:The Astrophysical Journal Letters

\begin{document}
\title{Data Mining in Nearby Galaxies}
\author[S. Rahmani, et. al.]{S.~Rahmani$^{1, 2}$\thanks{E-mail:
srahma49@uwo.ca}, H.~Teimoorinia$^{3}$, E.~Peeters$^{1, 2, 4}$, P.~Barmby$^{1, 2}$\\
$^{1}$Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada\\
$^{2}$Center for Planetary Science \& Exploration, Western University, London, ON N6A 3K7, Canada\\
$^{3}$Department of Physics $\&$ Astronomy, University of Victoria, Finnerty Road, Victoria, British Columbia, V8P 1A1, Canada\\
$^{4}$SETI Institute, 189 Bernardo Avenue, Suite 100, Mountain View, CA 94043, USA}
\maketitle

@@

%\import{../sections/}{caveat.tex}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Summery
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{SUMMARY}
\label{sec: summary}

We present results of studying spatially resolved regions in nearby galaxies using 
The Self-organizing maps both cluster data and show relative distance between each cluster. 
Therefore, we utilized it to find hidden subgroups in the data as well as finding relation between those groups.

Using smaller-sized self-organizing maps, the M31 data are clustered into two major groups, which lead us to correlations that could not have otherwise been seen without clustering.
We found that six of the regions in M31 create a subgroup of data, that have relatively lower amount of Mid- and far-infrared emission.
PAH fluxes in these regions are highly anti-correlated with \halpha, \sii, \oiii~and IRAC 5.8~$\mu$m emission, stellar mass and RHI.
These anti-correlations are insignificant when data from the whole galaxy are considered.
We discussed possible reasons for these anti-correlations and argued that the most probable reason to PAHs anti-correlate with optical emission and RHI is having harder radiation.
Harder radiation makes the size of H {\sc II} regions bigger and the size of PDRs smaller, which cause more \halpha~emission and less PAHs, respectively.

PAHs in clustered data also show anti-correlation with stellar mass.
We discussed the possibility of that higher stellar mass might destroy PAHs and as a result we see anti-correlation between them.
However, we did not find any correlation between 8/24~$\mu$m emission, as a tracer of PAH abundance, and stellar mass.
Unlike previous studies, we also did not find any correlation between 8/250~$\mu$m emission and stellar mass. 
This results show that PAHs in the clustered regions in M31, do not heated by old stellar populations.

In the maps with larger sizes, networks can be used to illustrate the relative relations of the regions with one another.
We found the relative similarity between M31 regions, by varying the size of networks.
A one-dimensional network with 14 neurons was needed in order to
separate all 10 regions; we concluded that some of the region in M31 (e.g. regions 4 and 7) have very similar properties.

A two-dimensional networks provide us a more complete picture of the data.
We created various subsets from input data and generated different networks which helped us to show a relative relations between regions in M31 more clearly.
We showed that region 10 always become isolated in networks, except when we only used PAHs data to create a network.
In that network region 10 blends more with other regions and only shows differences with data from region 8.
These results suggest that the PAHs in all 10 regions have almost the same properties.

% We introduced self-organizing maps as a method that can be used to predict the amount of various quantities based on the relative positions of the regions in the networks.
% By converting the relative distance between regions to the probability distribution function, we could predict unobserved/unmeasured properties of the galaxies with 10 per cent uncertainty.
We also applied the SOMs from M31 data to M101 data and found regions with similar properties in both galaxies placed in close regions in the SOMs.
We show that using this ability of the SOM, we can predict properties of regions in other nearby galaxies very fast.
We should note that we created our networks using values for 26 quantities from 10 regions in M31, which does not consider as a "big sample".
Increasing dimension of the data and the number of regions would help to have more reliable networks.
In future we can apply these networks on data from other nearby galaxies (e.g. M33 and M83), and learn about the properties of regions on those galaxies.

\section*{ACKNOWLEDGMENTS}
The authors thank A. Tammour for her useful comments. 
S.R., P.B., and E.P. acknowledge research support from the Natural Sciences and Engineering Research Council of Canada. This research has made use of the NASA/IPAC Extragalactic Database (NED), which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%biblio
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\bibliographystyle{mn2e}
\bibliography{ref_mining.bib}
\import{../sections/}{app_2d.tex}

### 2016-07-04 sections/data0.0.tex
draftv0.01

We gathered data from 10 regions in M31 (Fig.~\ref{fig: regions in m31}) and 8 regions in M101 (Fig.~\ref{fig: regions in m101}) as inputs for SOMs.
We chose those specific regions due to availability of the PAHs data for them.
Besides PAHs data, for each galaxy, we chose spectroscopy and photometry data as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
Table~\ref{tab: data} shows the full list of the data and their unit for both M31 and M101.
We divided each values by the area of their region (in arcsec$^2$), to remove the distance factor from the data compare values of quantities in both galaxies.
Since the resolution of the data varies from less than 1$\arcsec$ to $60\arcsec \times 90 \arcsec$, any attempt to match the resolutions causes loosing all the information in some of the input data (e.g. the spectroscopic data).
On the other hand, in this project we used flux (or value of the quantities) per area as inputs of SOMs, which the convolution methods conserve it~\citep{Aniano12}.
Therefore, we did not perform any resolution matching in this paper and used data in their original resolutions.

@@

  \begin{figure}
    \subfloat[MIPS 24~$\mu$m image of M31 from~\cite{Gordon06}, with position of 10 regions \label{fig: regions in m31}]{
      \includegraphics[width=0.5\textwidth]{../images0.0/M31/M31.png}
    }
    \hfill
    \subfloat[IRAC 3.6~$\mu$m image of M101~\cite{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
      \includegraphics[width=0.5\textwidth]{../images0.01/M101/M101.png}}
    \caption{Position of regions that the input data for SOM that obtained from there in M31 (up) and M101 (down).}
    \label{fig:dummy}
  \end{figure}

@@

     The 10 regions in M31 were chosen due to availability of the PAH data for them. 
     \cite{Dim15} studied PAH for those regions using {\it Spitzer}/Infrared Spectrograph~\citep[IRS,][]{Houck04b} observations. 
     They used {\sc PAHFIT IDL} tool~\citep{Smith07b} and measured fluxes and equivalent widths of PAH features as well as atomic line features.
     %For spectroscopy part of our sample, we utilized their measured fluxes for PAH lines. 
     \cite{Dim15} also measured metallicity and of radiation hardness index (RHI) for these 10 regions.
     We used the measured fluxes for PAHs featured, metallicity and RHI of each region as an input for SOMs.

     We used \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, [\sii] narrow badn and [\oiii] narrow band~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12} emission for photometry part of the sample.
     We changed units of all fluxes to Wm$^{-2}$ to be the same unit as PAHs fluxes.
     $^{12}$CO (J:$1\rightarrow0$) line~\citep{Nieten06} and the atomic gas (H\,{\sc I}) 21~cm emission from~\cite{Chemin09} were added to the input data. 
     For derived values, we utilized SFR(FUV + 24$\mu$m), stellar mass, mass of molecular clouds, mass of atomic gas (H\,{\sc I}), total gas mass, and total infrared (TIR) luminosity (L$_{\rm TIR}$) data from \cite{Rahmani16}, and L$_{\rm dust}$ and mass data from \cite{Draine14}.

    \subsection{M101 data}
    \label{Sec: data_M101_SOMN} 
     For M101 galaxy, we used PAH fluxes which had been measured using {\sc PAHFIT IDL} tool and reported in \cite{Gordon08}.
     We also added their measurement of metallicity and RHI for these regions to our sample.
     We used data available on NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather our photometry data of M101. 
     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS~24 and 70~$\mu$m~\cite{Dale09}, and  PACS~100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
     The Same as M31 data, we used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Helfer03} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Walter08} data.
     SFR(FUV + 24$\mu$m), stellar and total gas mass map were calculated using the same methods that M31 data were derived in \cite{Rahmani16}.

      Some of the correlations between some wavelengths and properties of galaxies are well-known.
     For example, \citep{Rahmani16} used IRAC1 band emission to calculate the stellar mass, or FUV, NUV and MIPS24 emission to measure the SFR values. 
     To make sure that we wouldn't use some of the observed data as an input data in various forms, we removed all the observed data, that were used to calculate these properties from the input sample.
     We used these sample as the main input for creating SOMs.
     Fig.~\ref{fig: cor_all} shows Pearson correlation coefficients with a confidence level of $95\%$ for the input data.

>>>>

We gathered data from 10 regions in M31 (Fig.~\ref{fig: regions in m31}) and 8 regions in M101 (Fig.~\ref{fig: regions in m101}) as inputs for SOMs.
We chose those specific regions due to availability of the PAH observations for them.
Besides PAH data, for each galaxy, we chose spectroscopy and photometry observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
Table~\ref{tab: data} shows the full list of the data and their unit for both M31 and M101.
We divided each value by the area of their region (in arcsec$^2$), to remove the distance factor from the data compare values of quantities in both galaxies.
Since the resolution of the data varies from less than 1$\arcsec$ to $60\arcsec \times 90 \arcsec$, any attempt to match the resolutions causes loosing all the information in some of the input data (e.g. the spectroscopic data).
On the other hand, in this project we used flux (or value of the quantities) per area as inputs of SOMs, which the convolution methods conserve~\citep{Aniano12}.
Therefore, we did not perform any resolution matching in this paper and used data in their original resolution.

@@

  \begin{figure}
    \subfloat[MIPS 24~$\mu$m image of M31 from~\cite{Gordon06}, with position of 10 regions \label{fig: regions in m31}]{
      \includegraphics[width=0.5\textwidth]{../images0.01/M31/M31.png}
    }
    \hfill
    \subfloat[IRAC 3.6~$\mu$m image of M101~\citep{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
      \includegraphics[width=0.5\textwidth]{../images0.01/M101/M101.png}}
    \caption{Position of regions that the input data for SOM that obtained from there in M31 (up) and M101 (down).}
    \label{fig:dummy}
  \end{figure}

@@

     The 10 regions in M31 were chosen due to availability of the PAH data for them. 
     \cite{Dim15} studied PAH for those regions using {\it Spitzer}/IRS observations. 
     They used~{\sc PAHFIT IDL} tool~\citep{Smith07b} and measured fluxes and equivalent widths of PAH features as well as atomic line features.
     %For spectroscopy part of our sample, we utilized their measured fluxes for PAH lines. 
     \cite{Dim15} also measured metallicity and radiation hardness index (RHI) for these 10 regions.
     We used the measured fluxes for PAH featured, metallicity and RHI of each region as an input for SOMs.

 We used \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, \sii~and \oiii narrow band~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12} emission for photometry part of the sample.
     We changed units of all fluxes to Wm$^{-2}$ to be the same unit as PAH fluxes.
     $^{12}$CO (J:$1\rightarrow0$) line~\citep{Nieten06} and the atomic gas (H\,{\sc I}) 21~cm emission from~\cite{Chemin09} were added to the input data. 
     For derived values, we utilized SFR(FUV + 24$\mu$m), stellar mass, mass of molecular clouds, mass of atomic gas (H\,{\sc I}), total gas mass, and total infrared (TIR) luminosity (L$_{\rm TIR}$) data from \cite{Rahmani16}, and L$_{\rm dust}$ and mass data from \cite{Draine14}.

    \subsection{M101 data}
    \label{Sec: data_M101_SOMN} 
     For M101, we used PAH fluxes which had been measured using {\sc PAHFIT IDL} tool and reported in \cite{Gordon08}.
     We also added their measurement of metallicity and RHI for these regions to our sample.
     We used data available on NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather our photometry data of M101. 
     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS~24 and 70~$\mu$m~\cite{Dale09}, and  PACS~100 and 160~$\mu$m and SPIRE~250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
     Similar to M31 data, we used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Helfer03} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Walter08}.
     SFR(FUV + 24$\mu$m), stellar and total gas mass map were calculated using the same methods that M31 data were derived in~\cite{Rahmani16}.

     Some of the correlations between some wavelengths and properties of galaxies are well-known.
     Emission in 3.6$\mu$m band traces the old stellar population very well~\citep[e.g]{Leitherer99,Smith07a} and it is used to calculate the stellar mass~\citep{Eskew12}.
     FUV, \halpha, and TIR emission are some of indicators of star forming regions.
     In this project we used SFR traced by FUV emission which corrected for foreground stars using NUV emission and for dust extinction using 24$\mu$m emission.
     TIR emission is calculated from modified version of~\cite{Draine07} calibration using using 8, 24, 70, and 160 $\mu$m emission~\citep{Boquien10}.
     To make sure that we do not use the observed data as an input data in various forms, we removed all the observed data, that were used to calculate properties of the galaxies from the input sample.
     We used these sample as the main input for creating SOMs.
     Fig.~\ref{fig: cor_all} shows Pearson correlation coefficients with a confidence level of $95\%$ for the input data.
